% Yuto Kawashima — Resume (Microsoft Solutions Engineer Intern)
% ! Build:  xelatex -jobname=Resume_Yuto_Kawashima resume.tex
%   (do NOT use pdflatex — fontspec requires XeLaTeX/LuaLaTeX)

\documentclass[10pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{xeCJK}
\setmainfont{Times New Roman}
\setCJKmainfont{Yu Mincho}[Scale=0.95]
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}

\geometry{margin=0.7in}
\setlength{\parindent}{0pt}
\setlist{leftmargin=*, nosep, itemsep=1pt}
\titlespacing*{\section}{0pt}{8pt}{4pt}
\titleformat{\section}{\normalfont\bfseries\large}{\thesection}{0.5em}{}[\titlerule]

\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  linkcolor=black,
  pdftitle={Yuto Kawashima - Resume},
  pdfauthor={Yuto Kawashima}
}

% ---------------------------------------------------------------------------
\begin{document}

% ---- Contact ----
\begin{center}
  {\LARGE \textbf{Yuto Kawashima}}\\[4pt]
  \href{mailto:yuto.k_1028@icloud.com}{yuto.k\_1028@icloud.com}
  \quad $|$ \quad
  \href{https://github.com/32Lwk}{github.com/32Lwk}
  \quad $|$ \quad
  \href{https://www.linkedin.com/in/kawashimayuto/}{linkedin.com/in/kawashimayuto}
  \quad $|$ \quad
  \href{https://www.yutok.dev/}{yutok.dev}
\end{center}
\vspace{2pt}

% ---- Objective (B+: real-world problems, bridge tech & user needs, SE-fit) ----
\section*{Objective}
Seeking to leverage technical depth to tackle real-world problems and deliver customer value by bridging technology and user needs, and communicating solutions clearly to stakeholders.

\vspace{2pt}

% ---- Education ----
\section*{Education}
\textbf{Nagoya University} \hfill Expected Graduation: Mar 2028\\
Faculty of Science, Department of Physics\\
Interests: Applied computing, simulation, and data-driven problem solving.\\
GPA: 3.22 / 4.0

\vspace{4pt}

% ---- Experience ----
\section*{Experience}
\textbf{Registered Sales Clerk (licensed to sell OTC pharmaceuticals in Japan)} \hfill Apr 2024 -- Present\\
\textit{Matsumotokiyoshi Co., Ltd.}
\begin{itemize}
  \item Listen to customer needs and provide tailored OTC medicine recommendations.
  \item Explain specialist product and safety information in accessible language.
  \item Collaborate with team members on inventory and daily operations.
\end{itemize}

\vspace{4pt}

% ---- Projects ----
\section*{Projects}
\textbf{Chat-based OTC Medicine Consultation Tool (Beta)}\\
\href{https://github.com/32Lwk/medicine-recommend-system}{GitHub}
$|$
\href{https://medicine-recommend-340042923793.asia-northeast1.run.app/}{Live Demo (JP UI; multilingual support available)}
\begin{itemize}
  \item Addressed real-world gaps (elderly communication, language barriers, staffing) with a chat app that suggests OTC medicines using a hybrid rule-based + LLM recommendation engine; full ownership from requirements to design, development, and operation.
  \item Tech: Python, Flask, OpenAI API, PostgreSQL (Neon), JS, GCP Cloud Run, Docker. Implemented security and input validation, multi-language and accessibility (WCAG-oriented) support.
  \item Migrated from Render to GCP Cloud Run and from Cloud SQL to Neon PostgreSQL; reduced cost and enabled scale-to-zero.
\end{itemize}

\textbf{Awards \& Competitions}
\begin{itemize}
  \item Yumekatari Student-Generated AI Contest: Development, Individual — \textbf{Grand Prize} (Nov 2025)
  \item Sugiyama Jogakuen University — 13th Business Plan Competition — \textbf{Excellence Award} (Dec 2025)
  \item 9th Wakayama Data Utilization Competition — \textbf{Quality Soft Award} (Dec 2025)
  \item Career Gateway 2025 Idea Competition (doda) — \textbf{Judge's Special Award} (Jan 2026)
\end{itemize}

\vspace{4pt}

% ---- Skills ----
\section*{Skills}
\textbf{Languages:} Python, JavaScript, HTML/CSS, TypeScript, Rust, C\\
\textbf{Frameworks:} Flask, Next.js, React, Tailwind CSS\\
\textbf{Cloud \& DevOps:} GCP (Cloud Run; design, deployment, operation), AWS, Docker; Azure (learning).\\
\textbf{Databases:} PostgreSQL\\
\textbf{Tools:} Git, GitHub, Linux

\vspace{4pt}

% ---- Certifications ----
\section*{Certifications}
Fundamental Information Technology Engineer Examination (Japan) \quad $|$ \quad
Registered Sales Clerk

\vspace{2pt}

% ---- Languages (optional compact line) ----
\section*{Languages}
Japanese (Native) \quad $|$ \quad
English: Intermediate (technical reading and documentation; conversational speaking)

\newpage
% ---- Statement of Purpose (for combined PDF submission) ----
\section*{Statement of Purpose}\vspace{6pt}
\subsection*{Japanese}
\textbf{テーマ：マイクロソフトで実現したいあなたの夢はなんですか？}\par\vspace{6pt}
私がマイクロソフトで実現したい夢は、技術を理解したうえで、社会に信頼される形で届けることです。この夢を、まず技術営業職として現場で体現したいと考え、応募しました。

私は和歌山県の過疎地で育ち、実家の近くにドラッグストアがなく、車がなければ薬を買いに行けない環境を目の当たりにしてきました。そして、私は大学で物理学を学びながらドラッグストアで「登録販売者」として勤務し、日々売り場に立っています。そこでは、薬選びに悩む様々な方に多く出会います。耳が遠く説明を聞き取れないご高齢の方や、言葉の壁があり症状を伝えられない外国人のお客様もいらっしゃいます。しかし、現場は慢性的な人手不足です。繁忙時には、お一人おひとりに十分な時間を割くことが難しく、そのたびに「もっと力になりたいのに」という歯がゆさを感じてきました。また近年、インターネットで薬が購入できる一方、相談先がないまま誤った薬を選んでしまうリスクもあります。このドラッグストアと過疎地の現状をテクノロジーで解決し、「誰もが安心して薬を選べるようにしたい」と考え、医薬品相談ツール（症状に応じたOTC医薬品の選択を支援するチャットアプリ）を個人で開発しました。また、現場では、ニーズを丁寧に聞き、専門情報を噛み砕いて伝えることの重要性を実感し、技術で課題を解決するだけでなく、届け方そのものが結果を変えると学びました。

一方で、つくったシステムが正しく使われるには、技術そのもの以上に、説明や前提の共有、相手との信頼関係が不可欠だと痛感しました。高齢者や多言語対応では、技術の良し悪しよりも「伝え方」で結果が大きく変わりました。開発だけでは社会に届かない。技術を深く理解したうえで、顧客の課題や文脈に合わせて価値として届け、意思決定を支える技術営業職の役割に強く魅力を感じ、志望しました。

マイクロソフトは、企業や社会インフラに深く関わるスケールがあり、技術とビジネスを分断しない文化に惹かれました。社会インフラに近い領域で、技術を価値として届ける経験ができると感じました。これまでGCPを用いた開発経験はありますが、技術が単体で存在するのではなく、業務や組織に組み込まれて価値を発揮するプロセスに強い関心を持っています。AzureやCopilotが、企業の現場でどのように活用され、意思決定や働き方の変革につながっているのかを、技術営業の立場で顧客と向き合いながら学びたいと考えています。

これまで、開発・ビジネスプラン・データ利活用などのコンペで、課題設定や提案・発表の経験を積んできました。インターンでは、お客様の課題をヒアリングし、技術でどう応えるかを設計し、提案やデモに落とし込む一連のプロセスと、営業をはじめ他職種との連携の実践を学びたいです。そのうえで、課題を言語化し、技術的背景を整理して説明する力を活かして貢献したいと考えています。

この2ヶ月で、この夢を胸に、技術営業職の現場で一歩を踏み出したいと考えています。この経験を土台に、社会や企業の基盤を支えるマイクロソフトの現場で、社会に信頼される技術者として歩み続けていきたいです。よろしくお願いいたします。

\newpage
\subsection*{English (same content)}
\textbf{Theme: What is your dream you want to realize at Microsoft?}\par\vspace{6pt}

My dream at Microsoft is to understand technology deeply and deliver it to society in a way that earns trust. I applied because I want to live that dream first as a Solutions Engineer in the field.

I grew up in a rural area of Wakayama Prefecture where access to pharmacies was limited—without a car, we could not easily buy even basic medicine. While studying physics at university, I have been working as a Registered Sales Clerk (licensed to sell OTC pharmaceuticals in Japan) at a drugstore and spending my days on the sales floor. There I meet many people who struggle to choose the right medicine: elderly customers who have difficulty hearing my explanations, and non-Japanese speakers who cannot easily describe their symptoms. The store, however, is chronically short-staffed. During busy periods, I often cannot give each customer enough time, and I often felt frustrated that I couldn't do more for each customer. In recent years, medicines have become easier to buy online, but the risk of choosing the wrong product without professional advice has also grown. I wanted to address this gap—both in the drugstore and in underserved areas—with technology, so I developed on my own a chat-based medicine consultation tool that helps users choose OTC products based on their symptoms. Through this experience at the store, I also learned how important it is to listen carefully to people's needs and to explain specialist information in plain language; I came to see that not only the solution itself but the way we deliver it changes the outcome.

At the same time, I realized that for a system to be used correctly, explanation, shared assumptions, and trust with the person using it matter more than the technology alone. With elderly users and multilingual support, the outcome depended more on \emph{how} we communicated than on the technical design. Technology alone does not reach society. I was drawn to the role of Solutions Engineer: understanding technology deeply, then delivering value that fits each customer's context and supporting their decisions.

Microsoft's scale and impact on enterprise and societal infrastructure, and its culture that does not separate technology from business, attracted me. I felt I could gain experience delivering technology as value in areas close to that infrastructure. I have built and operated systems on GCP, but I am especially interested in how technology creates value only when it is properly integrated into business workflows and decision-making processes. I want to learn, from the perspective of a Solutions Engineer working with customers, how Azure and Copilot are used in real business settings and how they connect to better decisions and transformation in how people work.

I have taken part in competitions in software development, business planning, and data utilization, where I practiced defining problems, proposing solutions, and presenting. During the internship, I want to learn the end-to-end process: hearing customers' challenges, designing how technology can address them, and turning that into proposals and demos, as well as working closely with sales and other roles. On that basis, I would like to contribute by putting challenges into words and explaining the technical context clearly.

I hope to take this two-month opportunity to take my first step as a Solutions Engineer with this dream in mind. I want to build on this experience and continue growing as a technologist who is trusted by society, in a place like Microsoft where the foundations of society and business are supported. Thank you for your consideration.

\end{document}
